\documentclass[12pt,a4paper]{article}

% ── Packages ──
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{parskip}

% ── Colors ──
\definecolor{huaweiRed}{HTML}{C7000B}
\definecolor{cyanAccent}{HTML}{00D4FF}
\definecolor{darkBg}{HTML}{1A1A2E}

\hypersetup{
    colorlinks=true,
    linkcolor=huaweiRed,
    urlcolor=cyanAccent,
}

% ── Header/Footer ──
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{huaweiRed}{\textbf{HUAWEI TECH4CONNECT}}}
\fancyhead[R]{\textcolor{gray}{Team Lafabrica}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ── Title Formatting ──
\titleformat{\section}{\Large\bfseries\color{huaweiRed}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries\color{darkBg}}{}{0em}{}

% ── Document ──
\begin{document}

% ── Title Page ──
\begin{titlepage}
    \centering
    \vspace*{3cm}
    {\Huge\bfseries\textcolor{huaweiRed}{HUAWEI TECH4CONNECT}\par}
    \vspace{0.5cm}
    {\Large Smart City Energy Management Platform\par}
    \vspace{2cm}
    {\large\textbf{Team Lafabrica}\par}
    \vspace{0.5cm}
    {\large Huawei ICT Solutions Showcase\par}
    \vspace{3cm}
    {\large\textit{Technical Documentation}\par}
    \vspace{1cm}
    {\large \today\par}
    \vfill
\end{titlepage}

\tableofcontents
\newpage

% ═══════════════════════════════════════════════════════════
\section{Project Overview}
% ═══════════════════════════════════════════════════════════

HUAWEI TECH4CONNECT is an interactive web platform showcasing a smart city energy management system for Algeria. It demonstrates how \textbf{piezoelectric energy} (harvested from footsteps) and \textbf{solar power} converge into a sustainable, bidirectional energy grid.

The platform monitors, predicts, and optimizes power distribution through real-time data visualization and immersive 3D interfaces, leveraging Huawei ICT solutions for sustainable urban energy infrastructure.

\subsection{Key Objectives}
\begin{itemize}
    \item Visualize dual-source energy harvesting (piezoelectric + solar)
    \item Provide real-time energy analytics and 48-hour forecasting
    \item Demonstrate smart grid bidirectional power flow
    \item Showcase geographic energy performance across Algerian regions
    \item Deliver an immersive, interactive 3D experience
\end{itemize}

% ═══════════════════════════════════════════════════════════
\section{Technology Stack}
% ═══════════════════════════════════════════════════════════

\subsection{Frontend Framework}
\begin{tabular}{@{}ll@{}}
    \toprule
    \textbf{Technology} & \textbf{Version} \\
    \midrule
    React              & 19.2.0 \\
    Vite               & 7.3.1 \\
    React Router DOM   & 7.13.1 \\
    \bottomrule
\end{tabular}

\subsection{3D Graphics \& Visualization}
\begin{tabular}{@{}ll@{}}
    \toprule
    \textbf{Library} & \textbf{Version} \\
    \midrule
    Three.js                      & 0.183.2 \\
    React Three Fiber             & 9.5.0 \\
    React Three Drei              & 10.7.7 \\
    React Three Postprocessing    & 3.0.4 \\
    \bottomrule
\end{tabular}

\subsection{Data Visualization}
\begin{tabular}{@{}ll@{}}
    \toprule
    \textbf{Library} & \textbf{Version} \\
    \midrule
    Recharts & 3.8.0 \\
    \bottomrule
\end{tabular}

\subsection{Development Tools}
\begin{tabular}{@{}ll@{}}
    \toprule
    \textbf{Tool} & \textbf{Version} \\
    \midrule
    ESLint     & 9.39.1 \\
    TypeScript & (type support) \\
    \bottomrule
\end{tabular}

% ═══════════════════════════════════════════════════════════
\section{Architecture}
% ═══════════════════════════════════════════════════════════

The application is a single-page application (SPA) built with React and served by Vite. The main layout renders all sections sequentially as a scrollable page.

\subsection{Application Flow}

\begin{verbatim}
User Entry
  |
  v
[Navbar]         -- Fixed navigation with smooth scroll
  |
  v
[Hero]           -- 3D intro with scroll/mouse parallax
  |
  v
[Dashboard]      -- Real-time energy analytics
  |
  v
[HexSimulation]  -- Piezoelectric floor demo
  |
  v
[PowerGrid]      -- SVG energy flow diagram
  |
  v
[House]          -- 3D smart city model
  |
  v
[Battery]        -- 3D energy storage visualization
  |
  v
[AlgeriaMap]     -- Geographic PED performance
\end{verbatim}

\subsection{State Management Strategy}
\begin{itemize}
    \item \textbf{Refs} for high-frequency updates (scroll position, mouse coordinates) to avoid React re-renders.
    \item \textbf{Intersection Observer} (\texttt{useInView} hook) for lazy-loading heavy 3D canvases.
    \item \textbf{Global state object} (\texttt{globalFootState}) synchronizes character foot positions with floor tile interactions in the simulation.
\end{itemize}

% ═══════════════════════════════════════════════════════════
\section{Components}
% ═══════════════════════════════════════════════════════════

\subsection{Navbar}
\textbf{File:} \texttt{src/components/Navbar/Navbar.jsx}

Fixed-position header providing Huawei \& TECH4CONNECT branding with smooth-scroll navigation to page sections (Home, About Us, Dashboard, Demo).

\subsection{Hero Section}
\textbf{Files:} \texttt{src/components/Hero/Hero.jsx}, \texttt{Model3D.jsx}

Interactive landing section featuring:
\begin{itemize}
    \item \textbf{3D Huawei Logo:} GLB model (\texttt{/hueawi+name.glb}) with PBR materials, floating animation, and scroll-based vertical movement.
    \item \textbf{Particle System:} Two layers of particles with custom vertex/fragment shaders that repel from the cursor.
    \item \textbf{Bloom Post-processing:} Glow effect applied via \texttt{@react-three/postprocessing}.
    \item \textbf{Scroll Parallax:} Model tilts and rises as the user scrolls; tracked via refs (no re-renders).
\end{itemize}

\subsection{PED Dashboard}
\textbf{File:} \texttt{src/components/Dashboard/PEDDashboard.jsx}

Comprehensive energy analytics panel providing:
\begin{itemize}
    \item \textbf{48-hour Forecasting:} Solar, piezoelectric, and demand predictions displayed on a line chart with past/future data split.
    \item \textbf{Building Analytics:} 15 buildings tracked with solar generation, piezo input, demand, comfort index (72--97\%), and surplus/deficit status.
    \item \textbf{Anomaly Detection:} Identifies solar underperformance and consumption spikes.
    \item \textbf{Multi-chart Interface:}
    \begin{itemize}
        \item Line chart --- Hourly energy forecast
        \item Pie chart --- Energy source distribution
        \item Bar chart --- Building performance comparison
        \item Area chart --- Demand curve
    \end{itemize}
    \item \textbf{Wilaya Map Overlay:} Displays 20 Algerian regions with seasonal PED scores.
\end{itemize}

\subsection{Hexagonal Floor Simulation}
\textbf{Files:} \texttt{src/components/HexSimulation/HexSimulation.jsx}, \texttt{HexSimulationScene.jsx}

Piezoelectric floor demonstration titled \textit{``Footsteps to Electricity''}:
\begin{itemize}
    \item \textbf{Tile Grid:} $\sim$336 triangular metal tiles arranged in a 28$\times$12 grid.
    \item \textbf{Character Model:} Walking animation on the floor with real-time foot position tracking.
    \item \textbf{Tile Interaction:} Tiles sink (0.055 units depth) and transition from gray to red when stepped on, with damping recovery.
    \item \textbf{Procedural Textures:} Metal and bump maps generated via the Canvas API.
    \item \textbf{Rendering:} Orthographic camera, cached shared geometry, local clipping planes.
\end{itemize}

\subsection{Power Grid Visualization}
\textbf{File:} \texttt{src/components/PowerGrid/PowerGrid.jsx}

Animated SVG diagram showing dual-source energy flow:
\begin{itemize}
    \item \textcolor{blue}{\textbf{Blue wires:}} Footsteps $\rightarrow$ Battery
    \item \textcolor{red}{\textbf{Red wires:}} Solar panels $\rightarrow$ Battery
    \item \textcolor{cyan}{\textbf{Cyan indicators:}} Battery $\leftrightarrow$ City (bidirectional)
\end{itemize}
Pulsing wire animations with staggered delays visualize energy convergence at the central battery hub.

\subsection{Smart City (House)}
\textbf{File:} \texttt{src/components/House/House.jsx}

3D city model (\texttt{/city.glb}) with:
\begin{itemize}
    \item Gentle continuous rotation and floating animation.
    \item Colored accent lights (cyan + red) for a sci-fi aesthetic.
    \item Lazy-loaded via \texttt{useInView} --- renders only when visible in viewport.
\end{itemize}

\subsection{Battery Storage}
\textbf{File:} \texttt{src/components/Battery/Battery.jsx}

Three battery models (\texttt{/battery.glb}) rendered side-by-side with:
\begin{itemize}
    \item Pointer-based parallax rotation responding to mouse movement.
    \item Float animation with scale effects.
    \item Lazy-loaded with demand-based frame rendering.
\end{itemize}

\subsection{Algeria Map}
\textbf{File:} \texttt{src/components/AlgeriaMap/AlgeriaMap.jsx}

Interactive SVG map of Algeria featuring:
\begin{itemize}
    \item 20 wilaya (region) markers with PED scores.
    \item Season selector (summer, spring, autumn, winter) affecting displayed data.
    \item Color-coded performance:
    \begin{itemize}
        \item \textcolor{green}{\textbf{Green}} --- Excellent ($\geq 85$)
        \item \textcolor{yellow}{\textbf{Gold}} --- Good (70--85)
        \item \textcolor{red}{\textbf{Red}} --- Poor ($< 70$)
    \end{itemize}
    \item Surplus MW generation display per region.
\end{itemize}

% ═══════════════════════════════════════════════════════════
\section{Custom Hooks}
% ═══════════════════════════════════════════════════════════

\subsection{useInView}
\textbf{File:} \texttt{src/hooks/useInView.js}

An Intersection Observer--based hook that returns a boolean indicating whether a referenced DOM element is visible in the viewport. Used to lazy-mount heavy 3D \texttt{<Canvas>} components, preventing GPU resource consumption for off-screen scenes.

% ═══════════════════════════════════════════════════════════
\section{Performance Optimizations}
% ═══════════════════════════════════════════════════════════

\begin{itemize}
    \item \textbf{Ref-based scroll tracking:} Scroll and mouse positions stored in refs instead of state, eliminating React re-renders during high-frequency events.
    \item \textbf{Lazy canvas mounting:} 3D scenes render only when visible in the viewport via Intersection Observer.
    \item \textbf{Cached geometries:} Shared triangle geometry instance reused across all 336 floor tiles.
    \item \textbf{Demand-based rendering:} Canvases configured with \texttt{frameloop="demand"}, updating only when necessary.
    \item \textbf{Asset preloading:} GLB models preloaded in \texttt{main.jsx} before the app mounts.
    \item \textbf{DPR cap at 1.5:} Prevents excessive pixel rendering on high-DPI displays.
    \item \textbf{Local clipping planes:} Prevents rendering artifacts at tile boundaries in the simulation.
\end{itemize}

% ═══════════════════════════════════════════════════════════
\section{3D \& Graphics Techniques}
% ═══════════════════════════════════════════════════════════

\begin{itemize}
    \item \textbf{Procedural textures:} Metal and bump maps generated at runtime via the HTML Canvas API.
    \item \textbf{Custom shaders:} GLSL vertex and fragment shaders for the particle repulsion system.
    \item \textbf{Bloom post-processing:} \texttt{EffectComposer} with \texttt{Bloom} pass for glowing neon effects.
    \item \textbf{Orthographic projection:} Used for the hexagonal floor to maintain geometric precision.
    \item \textbf{PBR materials:} Correct color space assignment (\texttt{SRGBColorSpace}) for physically-based rendering.
    \item \textbf{Animation system:} Three.js \texttt{AnimationMixer} for character walk cycles and model animations.
\end{itemize}

% ═══════════════════════════════════════════════════════════
\section{File Reference}
% ═══════════════════════════════════════════════════════════

\begin{longtable}{@{}p{6.5cm}p{8cm}@{}}
    \toprule
    \textbf{File} & \textbf{Purpose} \\
    \midrule
    \endhead
    \texttt{src/main.jsx}                                  & React entry point; GLB asset preloading \\
    \texttt{src/App.jsx}                                   & Main app layout, routing, About section \\
    \texttt{src/hooks/useInView.js}                        & Intersection Observer hook \\
    \texttt{src/components/Navbar/Navbar.jsx}               & Header navigation \\
    \texttt{src/components/Hero/Hero.jsx}                   & Hero parallax section \\
    \texttt{src/components/Hero/Model3D.jsx}                & 3D Huawei logo model \\
    \texttt{src/components/Dashboard/PEDDashboard.jsx}      & Energy analytics dashboard \\
    \texttt{src/components/HexSimulation/HexSimulation.jsx} & Piezoelectric floor container \\
    \texttt{src/components/HexSimulation/HexSimulationScene.jsx} & Floor physics \& character interaction \\
    \texttt{src/components/House/House.jsx}                 & 3D smart city model \\
    \texttt{src/components/PowerGrid/PowerGrid.jsx}         & Animated SVG energy flow \\
    \texttt{src/components/Battery/Battery.jsx}             & 3D battery storage visualization \\
    \texttt{src/components/AlgeriaMap/AlgeriaMap.jsx}       & Interactive map with PED metrics \\
    \bottomrule
\end{longtable}

% ═══════════════════════════════════════════════════════════
\section{Getting Started}
% ═══════════════════════════════════════════════════════════

\subsection{Prerequisites}
\begin{itemize}
    \item Node.js (v18+ recommended)
    \item npm or yarn
\end{itemize}

\subsection{Installation}
\begin{verbatim}
git clone https://github.com/CertifiedCodeBoy/HUAWEI-TECH4CONNECT.git
cd HUAWEI-TECH4CONNECT
npm install
\end{verbatim}

\subsection{Development Server}
\begin{verbatim}
npm run dev
\end{verbatim}

\subsection{Production Build}
\begin{verbatim}
npm run build
npm run preview
\end{verbatim}

\end{document}
